Supplemental Information: remote sensing riverine gas exchange and carbon efflux in ungauged rivers from SWOT observations

### 2021-06-04 supp_v3.Rmd
some ms updates

![Figure S2. k600 versus the turbulent dissipation rate eD using the data from @ulsethDistinctAirWater2019a. Colors correspond to whether a measurement is SWOT-observable, i.e. the river's width is > 50m. The k600 ~ eD model fundamentally breaks down in SWOT-observable rivers](cache/k600/roughness_theory/eM_k600.jpg)

@@

![Figure S4: plot of overall BIKER uncertainity](cache/validation/riverProperties_kge.jpg)

@@

![Figure S6: BIKER performance, defined by NRMSE (see Table 1 in the main text for the metric definition) versus mean river ko2, width, and slope.](cache/validation/riverProperties_kge.jpg)

![Figure S7: BIKER performance, defined by RRMSE (see Table 1 in the main text for the metric definition) versus mean river ko2, width, and slope.](cache/validation/riverProperties_kge.jpg)

@@

|**Name**|**Equation**|**Description**|**Reference**|
|-------------|-------------|-------------|-------------|-------------|
|Raymond 2012|$ln(V)=-1.64+0.285ln(Q)$|Trained on their dataset|@raymondScalingGasTransfer2012a|
|Raymond 2013|$ln(V)=mean(-1.64+0.285ln(Q),  -1.06+0.12ln(Q))$ |Average of the Raymond 2012 equation and one trained on 9,811 USGS streamgauges|@raymondGlobalCarbonDioxide2013a|
|Lauerwald 2015|$ln(V)=-1.06+0.12ln(Q)$ |Borrowed from 1/2 of the Raymond 2013 calculation (trained on 9,811 USGS streamgauges)|@lauerwaldSpatialPatternsCO22015|

>>>>

![Figure S2. k600 versus the turbulent dissipation rate eD using the data from @ulsethDistinctAirWater2019a. Colors correspond to whether a measurement is SWOT-observable, i.e. the river's width is > 100m. The k600 ~ eD model fundamentally breaks down in SWOT-observable rivers](cache/k_eD/eD_k600.jpg)

@@

![Figure S4: plot of overall BIKER uncertainity. THESE ARE STAND IN RESULTS AND NEED TO BE UPDATED](cache/MonteCarlo/MC_results.jpg)

@@

![Figure S6: BIKER performance, defined by NRMSE (see Table 1 in the main text for the metric definition) versus mean river ko2, width, and slope.](cache/validation/riverProperties_nrmse.jpg)

![Figure S7: BIKER performance, defined by RRMSE (see Table 1 in the main text for the metric definition) versus mean river ko2, width, and slope.](cache/validation/riverProperties_rrmse.jpg)

@@

|**Name**|**Equation**|**Description**|**Reference**|
|-------------|-------------|-------------|-------------|-------------|
|Raymond 2012|$D=0.409Q^{0.294}$|1,026 measurements across the United States|@raymondScalingGasTransfer2012a|
|Raymond 2013|$D=0.409Q^{0.294},  D=0.449Q^{0.37}$ |Average of the Raymond 2012 equation and one using 9,811 measurements at US streamgauges|@raymondGlobalCarbonDioxide2013a|
|Lauerwald 2015|$D=0.449Q^{0.37}$ |Borrowed from 1/2 of the Raymond 2013 calculation (trained on 9,811 measurements at US streamgauges). This was used on all rivers of at least stream order 4, which we assume applies to all of these SWOT-observable rivers|@lauerwaldSpatialPatternsCO22015|
|Horgby 2019|$D=0.298Q^{0.222}$ |141 measurements made in 12 mountain streams in the Swiss Alps|@horgbyUnexpectedLargeEvasion2019|
